Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-23 paper.tex
removed some fixed comments

\todo[inline]{The notation $\hcvOOinj{P}{v}$ is non-standard
   and should be explained. -JS
\\---\\
Fixed. -KC}

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{rclr}
  \stxrule{v}{values}{
    \hcvOOtt \mid
    \hcvOOfun{c}{\rho}{x}{e}{c} \mid
    \hcvOOcons{v}{c}{v}{c} \mid
    \hcvOOinl{v}{c} \mid
    \hcvOOinr{v}{c} \mid
    \hcvOOinj{P}{v}
  }
\stxrule{r}{cast results}{
  \rOOsucc{v} \mid
  \rOOfail{l}
}
  \end{array}
  \]
\end{definition}

\todo[inline]{We also need to define results $r$ for \effCEK{C} -JS
\\---\\
Fixed. -KC}

@@

We prove the equivalence among two \effCEK{C} machines with a strong
bisimulation. The bisimulation relation is the smallest congruence relation 
that also includes the pairs induced by the rules below.
\todo[inline]{By ``derived from the definitions'' do you mean
 that it is a congruence? -JS
\\---\\
Exactly, fixed. -KC}

@@

\begin{lemma}[Strong Bisimulation among $\mathcal{S}(\cdot)$]
  \label{thm:CEKS-bisim}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT
  $s_{1} \in \text{\effCEK{C_1}}$,
  $s_{2} \in \text{\effCEK{C_2}}$,
  $s_{1} \approx s_{2}$,
  \begin{enumerate}
    \item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
    \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
    \item If $\judgeSreduce{C_1}{s_1}{s_3}$ 
    then $\judgeSreduce{C_2}{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$
    \item If $\judgeSreduce{C_2}{s_2}{s_4}$ 
    then $\judgeSreduce{C_1}{s_1}{s_3}$ and $s_3 \approx s_4$ for some $s_3$
  \end{enumerate}
% 
  Or diagrammatically, 
  \[\begin{array}{clc}
  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_3\\
  \rotatebox[origin=c]{90}{$\approx$} 
  & & \rotatebox[origin=c]{90}{$\approx$} \\
  s_{2} & 
  \longrightarrow_{\text{\ineffCEKD}} & s_4 \\
  \end{array}\]
\end{lemma}
\begin{proof} By casing on $s_{1} \approx s_{2}$.
%
  \todo[inline]{The above sentence is not normal proof jargon.  Are
    you doing a proof by cases on $s_{1}
    \longrightarrow_{\text{\effCEK{C}}} s_1'$? -JS
\\---\\
By casing on the bisimulation relation. -KC}
%
  The key ideas of this proof are undoing sequencing with the property
  (2) of Lazy D Cast ADT, and handling all possibly uses of
  $cast(T,l,T)$ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
  Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
  $\judgeSreduce{C_2}{e}{o}$.\\
  By the definition of $eval_{\mathcal{S}(C)}$, we know 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
  have 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  that is, $\judgeSreduce{C_2}{e}{o}$
\todo[inline]{Induction on what? -JS
\\---\\
Fixed. -KC}
\end{proof}

@@

  \caption{The $L$ Lazy D Cast ADT}
\end{figure}

>>>>

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{rclr}
  \stxrule{v}{values}{
    \hcvOOtt \mid
    \hcvOOfun{c}{\rho}{x}{e}{c} \mid
    \hcvOOcons{v}{c}{v}{c} \mid
    \hcvOOinl{v}{c} \mid
    \hcvOOinr{v}{c} \mid
    \hcvOOinj{I}{v}
  }
\stxrule{r}{cast results}{
  \rOOsucc{v} \mid
  \rOOfail{l}
}
  \end{array}
  \]
\end{definition}

@@

We prove the equivalence among two \effCEK{C} machines with a strong
bisimulation. The bisimulation relation is the smallest congruence relation 
that also includes the pairs induced by the rules below.

@@

\begin{lemma}[Strong Bisimulation among $\mathcal{S}(\cdot)$]
  \label{thm:CEKS-bisim}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT
  $s_{1} \in \text{\effCEK{C_1}}$,
  $s_{2} \in \text{\effCEK{C_2}}$,
  $s_{1} \approx s_{2}$,
  \begin{enumerate}
    \item If $s_1 = \sOOhalt{o}$ then $s_2 = \sOOhalt{o}$
    \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
    \item If $\judgeSreduce{C_1}{s_1}{s_3}$ 
    then $\judgeSreduce{C_2}{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$
    \item If $\judgeSreduce{C_2}{s_2}{s_4}$ 
    then $\judgeSreduce{C_1}{s_1}{s_3}$ and $s_3 \approx s_4$ for some $s_3$
  \end{enumerate}
% 
  Or diagrammatically, 
  \[\begin{array}{clc}
  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_3\\
  \rotatebox[origin=c]{90}{$\approx$} 
  & & \rotatebox[origin=c]{90}{$\approx$} \\
  s_{2} & 
  \longrightarrow_{\text{\ineffCEKD}} & s_4 \\
  \end{array}\]
\end{lemma}
\begin{proof} By cases on $s_{1} \approx s_{2}$.
%
  The key ideas of this proof are undoing sequencing with the property
  (2) of Lazy D Cast ADT, and handling all possibly uses of
  $cast(T,l,T)$ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
  Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
  $\judgeSreduce{C_2}{e}{o}$.\\
  By the definition of $eval_{\mathcal{S}(C)}$, we know 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
  have 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  that is, $\judgeSreduce{C_2}{e}{o}$
\end{proof}

@@

\caption{The $L$ Lazy D Cast ADT}
\label{fig:L-instance-LazyD}
\end{figure}

The $L$ cast representation is defined in
\figref{fig:L-instance-LazyD}.

\todo[inline]{KC, please write a 2-3 sentence overview of
  the $L$ cast representation. -JS}
